RJObject Paper

### 2014-06-08 Documents/Paper/ms.tex
Starting to describe the problem
Hierarchical

\section{Introduction}
Many inference problems have the following structure.

>>>>

\section{Introduction}
Many inference problems have the following structure. There is some unknown
number, $N$, of objects in a region. Each of the $N$ objects has a property
$x$, which may be a single scalar value (for example, a mass), or a set of
values (e.g. a position and a mass).

We would like to assign a prior to the objects' properties $\{x_i\}_{i=1}^N$.
Since $N$ may be large, it is usually easier to assign an ``interim prior''
conditional on some hyperparameters $\alpha$.
